---
title: "LDI 주식 Monitoring"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. 매크로 factors
PMI
매크로 레벨과 심리를 신속하게 파악할 수 있는 PMI 지표의 최근 변화를 점검 - 주가 수익률과의 비교를 통해 경제-주식시장 연계성이나 괴리를 파악

```{r Macro, echo=FALSE, warning=FALSE}
library(dygraphs)
library(knitr)
pmi <- readRDS("C:/Users/User/Documents/montoring_template/PMI.RDS")
esi <- readRDS("C:/Users/User/Documents/montoring_template/ESI.RDS")
gdp <- readRDS("C:/Users/User/Documents/montoring_template/GDP.RDS")

dygraph(pmi, main = "제조업 Global PMI") %>%
  dyRangeSelector()
kable(tail(as.data.frame(pmi),5), caption = "제조업 Global PMI")

dygraph(esi, main = "Economic Surprise Index") %>%
  dyRangeSelector()
kable(tail(as.data.frame(esi),5), caption = "Economic Surprise Index")

dygraph(gdp, main = "JPM GDP forecast") %>%
  dyRangeSelector()
kable(tail(as.data.frame(gdp),5), caption = "JPM GDP forecast")
```

## 2. 유동성

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


## 3. Earnings

## 4. Valuation

## 5. Rotation

a. Countries Rotation
```{r time series labels, echo=FALSE}


```
b. Sectors Rotation

## 6. Technicals

## 7. Risk Monitors

a. Cross assets

b. Risk On/Off

c. Financial stress
